% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/huajh/huajh-awesome-latex-cv
%
% Author:
% Junhao Hua


%Section: Publications
\sectionTitle{\textsc{Publications \& patent}}{\faLeanpub}
{\fontsize{13pt}\textbf{\textsc{Journal Articles}} }
\begin{itemize}
	\item Zhengrong Xu, \textbf{Rudan Xiao}, Dianwu Liu, ``eRF3b-37 inhibits the TGF-β1-induced activation of hepatic stellate cells by regulating cell proliferation, G0/G1 arrest, apoptosis and migration,''  \emph{Int J Mol Med}. DOI: 10.3892/ijmm.2018.3900.
	
	\item Yadong Yang, Tao Zhang, \textbf{Rudan Xiao}, ``Platform-independent approach for cancer detection from gene expression profiles of peripheral blood cells,''  \emph{Briefings in Bioinformatics}. DOI: 10.1093/bib/bbz027.
	\textbf{(co-first author)}
	
	\item \textbf{Rudan Xiao}, Yunxiao Ren, Xiangdong Fang, ``The Advances of Gene Editing in the treatment of Sickle Cell Anemia,'' \emph{J Development Med}.   DOI: 10.3969/j.issn.2095-5340.2018.03.003. \textbf{(first author)}
	
	\item Lan Ren, \textbf{Rudan Xiao}, Qian Zhang, ``The synergistic regulation of K562 cells erythroid differentiation by KLF1 and KLF9,'' \emph{Hereditas Beijing}. DOI: 10.16288/j.yczz.18-174. \textbf{(co-first author)}
	
	\item Yunxiao Ren, \textbf{Rudan Xiao}, Xiaomin Lou, ``The Research Advances and Application in Gene Editing Technology ,''\emph{Hereditas Beijing} . DOI: 10.16288/j.yczz.18-142. \textbf{(second author)}
	
	\item Xunong Dong, \textbf{Rudan Xiao}, Junwei Zhu, ``miR-185-5p as a Potential Regulator for Erythroid Differentiation in Human Embryonic Stem Cells and Erythroid Cells,'' In preparation.
	
\end{itemize}

{\fontsize{13pt}\textbf{\textsc{Books and Chapters}} }
\begin{itemize}
	\item Fang,X.D.& Hu,S.N.(Eds.). (2017). \emph{Transcriptomics and Precision Medicine}. \textbf{Chapter4:} Application of transcriptomics in the diagnosis and treatment of malignant tumors, Page:104-134. 
	\item He,L.& Fang,X.D.(Eds.).(2018). \emph{Genetic Counseling Today}. \textbf{Chapter 8.4.1:} Bioinformatics databases and platforms for genomic variation \& \textbf{Chapter 8.4.2:} Bioinformatics databases and platforms for epigenetic modified and non-coding RNA variants. 
\end{itemize}

{\fontsize{13pt}\textbf{\textsc{patent}} }
\begin{itemize}
	\item Obtained the \textbf{software copyright} of genetic risk assessment system for cervical cancer, colorectal cancer and type 2 diabetes.
\end{itemize}