% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/huajh/huajh-awesome-latex-cv
%
% Author:
% Junhao Hua


%Section: Work Experience at the top
\sectionTitle{\textsc{Projects \& Experiences}}{\faCode}
 
\begin{experiences}
	
		
 \experience
    {now}   {Master project}{Bioinformatics}{Multi-omics Integration}
    {Aug. 2017} {
                      \begin{itemize}
                        \item Explored the pathogenesis of Diamond-Blackfan anemia by integrating transcriptome and genomic data to make it more reliable than traditional single-omic analysis.
                      \end{itemize}
                    }
                        {FastQC,HISAT2,StringTie,Samtools,miRDeep2,STAR-Fusion,GATK,Plink,IPA,R,Python, Perl}

  \emptySeparator
  \experience
    {Oct. 2018} {Master project}{Bioinformatics and Cell Experiment}{Function of microRNA-185}
    {Dec. 2017}    {
                      \begin{itemize}
                        \item Verified the fuction of miR-185 in hematopoietic stem cell differentiation. 
          
                      \end{itemize}
                    }
                       {bowtie2,mirDeep2,miRDB,SPSS,stem cell culture,lentiviral packaging and infection,flow cytometry,PCR,qPCR,western blot,Benzidine dyeing,Giemsa staining}

  \emptySeparator
  \experience
    {Mar. 2018} {Master project}{Machine Learning}{Breast Cancer Detection Model}
    {Aug. 2016}    {
                      \begin{itemize}
                        \item Established a effective model for breast cancer detection, which is suitable for integrating different batches of gene expression data on different platforms. 
                        \item Used a variety of machine learning methods for feature selection and classification, such as recursive feature elimination, elastic network, random logistic regression, random forest and Naive Bayes, etc.               
                      \end{itemize}
                    }
                       {R,Python,Perl,Git}

  \emptySeparator
  \experience
  {Aug. 2017} {Master project}{Software Engineering}{Genetic Risk Assessment System}
  {Aug. 2016}    {
				  	\begin{itemize}
				  		\item Established a genetic risk assessment system for cervical cancer, colorectal cancer and diabetes.
				  	\end{itemize}
				  }
				      {Rstudio,Shiny,Git}
				  
  \emptySeparator
  \experience
  {Jul. 2016} {Clinic Intern}{Medicine}{Clinical Department Rotation}
  {Aug. 2015}    {
  	\begin{itemize}
  		\item Interned in Shijiazhuang Fifth Hospital, People's Hospital of Shijiazhuang and Center for Disease Control of Beijing Military Region.
  		\item  Rotated in Internal Medicine, Surgery, Pediatrics and Radiology, etc.
  	\end{itemize}
  }
      {Epidemiological investigation, Data collection, Image report,Pathology slice, Surgical assistant}

  \emptySeparator
  \experience
    {Jun. 2015} {Bachelor project}{Basic Experiment}{hepatic stellate cells}
    {Aug. 2014}    {
                      \begin{itemize}
                        \item Verified the role of eRF3b-37 in the activation of hepatic stellate cells.
                      \end{itemize}
                    }
                       {cell culture, RT-qPcR, western blotting, ELISA,immunohistochemistry}

\end{experiences}

